Exploring the Relationship between Family Background and Children's Education Level in the United States (2021)

### 2023-04-18 outputs/paper/paper.qmd
changes based on the comments

417 add a paragraph for each section

# Data {#sec-data} (417 add the graph for data)

## Source
The 2021 General Social Survey (GSS) is a nationally representative survey conducted to collect data on social trends and attitudes among people living in the United States. Data was collected through face-to-face interviews with adult residents, covering a wide range of variables that are of interest to social scientists, policymakers, and the general public. The variables measured in the survey include demographics, employment, education, health, family, and social attitudes [@gss_data_explorer].

@@

@@

p1 + p2
```
In order to examine the relationship between parents' prestige scores and children's education level. The next plot, @fig-presandeduc, is used to show the relation. These two scatter plots show the father's prestige score and the mother's prestige score with their children's education. It is hard to see a clear relation or pattern based on these two scatter plots. To verify if the prestige score is one of the factors, a linear model will be used in the @sec-model.

@@

@@

# Model {#sec-model}

@@

# Discussion

@@

In this paper, by examining the average year of schooling in the United States, based on 2021 GSS data, it was found that the average year of schooling is 14 in @tbl-educ. This result is consistent with the findings from Our World in Data, which indicate that the average year of schooling in the US is also 14 years [@global_education].

@@

It's noteworthy that none of the top schools are from the Middle Atlantic or New England regions, which have positive coefficients in the model. This discrepancy could be due to differences in time. School rankings can change over the years as states develop, and the GSS respondents were born in a different time period. This leads to a mismatch between the rankings and the model's coefficients.

@@

## Weaknesses and next steps {#sec-weakness}

### Weaknesses

@@

### Next Steps

@@

# Appendix

>>>>

The structure of this paper comprises several sections. In the @sec-data, it introduces the source of the data and the cleaning process, as well as the characteristics of the variables. In the @sec-result, it reveals some findings from the data regarding how parents' backgrounds may affect children's education levels. In the @sec-discussion, it take a closer look at the results and compares them with the published researches. Additionally, the @sec-weakness lists some of the potential limitations of the paper and sheds light on future studies. The section of @sec-conclusion is the conclusion of the paper. Lastly, a mock survey related to the topic of this paper can be found in the @sec-appendix.

# Data {#sec-data}

## Source

The 2021 General Social Survey (GSS) is a nationally representative survey conducted to collect data on social trends and attitudes among people living in the United States. Data was collected through face-to-face interviews with adult residents, covering a wide range of variables that are of interest to social scientists, policymakers, and the general public. The variables measured in the survey include demographics, employment, education, health, family, and social attitudes [@gss_data_explorer].

@@

## Characteristics of the variables

@@

@@

p1 + p2
```

In order to examine the relationship between parents' prestige scores and children's education level. The next plot, @fig-presandeduc, is used to show the relation. These two scatter plots show the father's prestige score and the mother's prestige score with their children's education. It is hard to see a clear relation or pattern based on these two scatter plots. To verify if the prestige score is one of the factors, a linear model will be used in the @sec-model.

@@

## Model {#sec-model}

@@

# Discussion {#sec-discussion}

@@

In the previous paper, the average year of schooling in the United States, based on 2021 GSS data, it was found that the average year of schooling is 14.76 and the avergae now is 14.82 in @tbl-educ. Despite the tiny changes in numbers due to the multiple imputation, this result is still consistent with the findings from Our World in Data, which indicate that the average year of schooling in the US is also 14 years [@global_education].

@@

It is noteworthy that none of the top schools are from the Middle Atlantic or New England regions, which have positive coefficients in the model. This discrepancy could be due to differences in time. School rankings can change over the years as states develop, and the GSS respondents were born in a different time period. This leads to a mismatch between the rankings and the model's coefficients.

@@

# Weaknesses and next steps {#sec-weakness}

## Weaknesses

@@

## Next Steps

@@

# Conclusion {#sec-conclusion}

Education is a critical component in both social and economic progress. Therefore, understanding educational trends in the US has valuable implications for policymaking and decision-making. This paper examines the impact of family income level, parental education, and living regions during adolescence on children's education. Higher income levels are generally associated with higher education levels for children, and fathers' education levels have a stronger impact on their children's academic achievement than mothers' education levels. The influence of both parents is still significant.

Adolescent living environments also influence completion of a postsecondary degree. Although the results are not statistically significant, the Middle Atlantic and New England regions demonstrate a favourable connection with children's educational levels. These findings highlight the significance of parental involvement and support in children's education, with a particular emphasis on the role of fathers. Future research is needed to properly comprehend the complex relationship between these variables and their impact on children's educational attainment.

# Appendix {#sec-appendix}
